---
title: "R-script"
author: "Yi-Hsin Liu"
date: "2019/5/15"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  comment='')
library(formatR)
```

# Basic features of R  
  
## 1. Vectors  
> ``` c() ```

+ Creating a vector 
```{r vector creating}
x<-c(2,3,4,5,6)
x
```
  
+ Extracting elements from vectors
```{r vector extracting, tidy=TRUE, results='hold'}
x[2]
#extrcting all elements except the second element
x[-2]   
x[3:5]
```
  
+ Vector arithmetic
```{r vector ,tidy=TRUE, results='hold'}
x
x * 3
y <- x-5
y
x^3
y^x
```
+ Simple patterned vectors  
>```seq(from = 1, to = 1, by = ((to-from)/(length.out-1)), length.out = NULL, along.with = NULL, ...)```

```{r seq() function}
seq(1, 21, by=2)
seq(0, 1, len = 5)
```

> ```rep(x, times = 1, length.out = NA, each = 1)```

```{r rep() function}
rep(1:4, each = 2, len = 4)  #first four only
rep(c(1, 4), c(3, 2))  #repeat 1 : 3 times, and 4 :2 times
rep(seq(2, 10, 2), rep(2, 5))  #repeat each value twice

```

+ Character vectors  
  
> ```substr(x, start, stop)  paste(..., sep = " ", collapse = NULL)```  

```{r char vectors, results='hold'}
colors <- c("red", "yellow", "blue")
substr(colors, 1, 2)
paste(colors, "flowers")
paste("several", colors, "s", sep="")
paste("I like", colors, collapse=", ")
```

## 2. Factors
>```factor(x = character(), levels, labels = levels, exclude = NA, ordered = is.ordered(x), nmax = NA)``` 

```{r factor, results='hold'}
grp <- c("A", "B", "A", "B")
grp
grp2 <- factor(grp)
grp2
as.integer(grp2) #the levels of a factor are internally coded as integers 
levels(grp2)
grp2[3]
```

```{r factor2, results='hold', tidy=TRUE}
fac=c("AAAAA","ABABA","aaaaa","ABABA",111)
fac
#Map from 4 different values to three levels:
fac2=factor(fac, levels = c(111,"AAAAA","ABABA","aaaaa"),
                 labels = c(111,"AAAAA","ABABA","AAAAA"))
fac2
as.integer(fac2)
```

```{r factor3, results='hold'}
#omit the fifth element, but not omit from levels
fac3=fac2[-5]
fac3
as.integer(fac3)
levels(fac3)[c(1,2,1,2,3)]
```

## 3. Matrices and arrays  
> ```matrix(data = NA, nrow = 1, ncol = 1, byrow = FALSE, dimnames = NULL)```  

```{r matrices}
m <- matrix(1:6, nrow=2, ncol=3, dimnames=list(c("r1","r2"), c("c1", "c2","c3")))
m
m[1, 2]
m[4] #column-major storage order
m[1,] #whole rows
m[, 1] #whole columns
m[c(1,2), c(2,3)] #submatrix
m[c(1,2), c(2,3)] = 2*m[c(1,2), c(2,3)]
m
```

> ```array(data = NA, dim = length(data), dimnames = NULL)```  

```{r array}
a <- array(1:24,c(3, 4, 2))
a
```

## 4. Dataframes  
>```data.frame(..., row.names = NULL, check.rows = FALSE, check.names = TRUE, fix.empty.names = TRUE, stringsAsFactors = default.stringsAsFactors())```  
           
           
```{r dataframes}
color=c("red","red","red1","blue")
number=c(1,3,5,7)
logic=c(T,T,F,F)

fr <- data.frame(colors=color, numbers=number, logics=logic)
fr #naming each columns

fr2 <- data.frame(color,number,logics=logic)
fr2 #original names from vectors

fr["numbers"]
```
```{r, results='hold'}
#extract "numbers"
fr[,2]
fr[,"numbers"]
fr$number #numeric
#extract "colors"
fr$colors #factor
#extract "logics"
fr$logics #logical
```

## 5. Logical vectors  

Boolean |  A  |  B  | not A | not B | A and B | A or B 
------- | --- | --- | ----- | ----- | ------- | -------
R code  |  A  |  B  |  !A   |  !B   |  A & B  |  A \| B
T/F     |TRUE |TRUE |FALSE  |FALSE  |TRUE     |TRUE
T/F     |TRUE |FALSE|FALSE  |TRUE   |FALSE    |TRUE
T/F     |FALSE|TURE |TRUE   |FALSE  |FALSE    |TRUE
T/F     |FALSE|FALSE|TRUE   |TRUE   |FALSE    |FALSE  

```{r logical operations}
a <- c(TRUE, FALSE, FALSE, TRUE)
b <- c(13, 7, 8, 2)
c<-c(FALSE, TRUE, TRUE, FALSE)
d<-c(FALSE, FALSE)

b[a]
b||c
c||b
a&&b
d&&b
a & (b& c)
```

```{r relation operator}
a <- c(3, 6, 9)
a > 4
a == 4
a[a > 4]
b <- c(4, 6, 8)
a < b
a[a < b]
a[a <= b]
```

## 6. Lists  
```{r}
x <- c(3, 2, 3)
y <- c(7, 7)
new <- list(x = x, y = y)
new
names(new)
new$x[2]
```
***
# High-level plots  

## 1. Bar charts  
```barplot(height, width = 1, space = NULL, names.arg = NULL,```
        ```legend.text = NULL, beside = FALSE, horiz = FALSE,```  
        ```density = NULL, angle = 45, col = NULL, ```  
```        border = par("fg"), main = NULL, sub = NULL, ```  
```        xlab = NULL, ylab = NULL, xlim = NULL, ylim = NULL,```  
```        xpd = TRUE, log = "", axes = TRUE, axisnames = TRUE,```  
```        cex.axis = par("cex.axis"), cex.names = par("cex.axis"),```  
```        inside = TRUE, plot = TRUE, axis.lty = 0, offset = 0,```  
```        add = FALSE, args.legend = NULL, ...)```

```{r ,paged.print=TRUE}
VADeaths

barplot(VADeaths, beside=TRUE, legend=TRUE, ylim=c(0,90), ylab="Deaths per 1000", main="Death rates in Virginia")
```

## 2. Dot charts  
```{r dotchart}
dotchart(VADeaths, xlim=c(0,75),
xlab="Deaths per 1000", main="Death rates in Virginia")

```

## 3. Pie charts  
```{r pie}
groupsizes=c(18,30,32,10,10)
labels=c("甲","乙","丙","丁","戊")
pie(groupsizes,labels,col=c("grey40","white","grey","black","grey"))
```

## 4. Histograms  
```{r hist, paged.print=TRUE}
x=rnorm(100)
hist(x)

hist(x,breaks=5)
```

## 5. Box plots  
```{r boxplot, paged.print=TRUE, fig.show='hold'}
boxplot(Sepal.Length ~ Species, data=iris, ylab="Sepal length(cm)",
main="Iris measurments", boxwex=0.5) 

boxplot(Sepal.Length ~ Species, data=iris, ylab="Sepal length(cm)",
main="Iris measurments", boxwex=0.1) 
```

## 6. Scatter plots
```{r plot, paged.print=TRUE}
x <- rnorm(100)
y <- rpois(100,30)
mean(y)

plot(x,y, main="Poisson versus Normal")
plot(x, y, type="l")
plot(sort(x),sort(y), type="l")
```

## 7. QQ plots  
```{r qqplot, fig.show = "hold", fig.ncol = 2}
X <- rnorm(1000)
A <- rnorm(1000)
qqplot(X, A, main="A and X are the same")
B <- rnorm(1000, mean=3, sd=2)
qqplot(X, B, main="B is rescaled X")
C <- rt(1000, df=2)
qqplot(X, C, main="C has heavier tails")
D <- exp(rnorm(1000))
qqplot(X, D, main="D is skewed to the right")
```

# Low-level plots  

## 1. The plotting region and margins

```{r plotregion}
par(mar=c(4, 5, 6, 7) + 0.1)
plot(c(1,9), c(0,50), type="n", xlab="", ylab="")
text(6,40, "Plot region")
points(6,20)
text(6,20, "(6,20)", adj=c(0.5,2))
mtext(paste("Margin", 1:4), side=1:4, line=3)
mtext(paste("Line", 0:3), side=1, line=0:3, at=3, cex=0.6)
mtext(paste("Line", 0:4), side=2, line=0:4, at=15, cex=0.6)
mtext(paste("Line", 0:5), side=3, line=0:5, at=3, cex=0.6)
mtext(paste("Line", 0:6), side=4, line=0:6, at=15, cex=0.6)

```

## 2. Adding to plots  

```{r points}
indexfinger=read.table("d:/indexfinger.txt", header=T)

plot(width~length, data=indexfinger)

with(indexfinger[c(3,7),], points(length, width, pch=16))

with(indexfinger[c(1,4),], points(length, width, pch=10))
```

```{r pchShow, echo=FALSE}
pchShow <-
  function(extras = c("*",".", "o","O","0","+","-","|","%","#"),
           cex = 3, ## good for both .Device=="postscript" and "x11"
           col = "black", bg = "gold", coltext = "brown", cextext = 1.2,
           main = paste("plot symbols :  points (...  pch = *, cex =",
                        cex,")"))
  {
    nex <- length(extras)
    np  <- 26 + nex
    ipch <- 0:(np-1)
    k <- floor(sqrt(np))
    dd <- c(-1,1)/2
    rx <- dd + range(ix <- ipch %/% k)
    ry <- dd + range(iy <- 3 + (k-1)- ipch %% k)
    pch <- as.list(ipch) # list with integers & strings
    if(nex > 0) pch[26+ 1:nex] <- as.list(extras)
    plot(rx, ry, type = "n", axes  =  FALSE, xlab = "", ylab = "", main = main)
    abline(v = ix, h = iy, col = "lightgray", lty = "dotted")
    for(i in 1:np) {
      pc <- pch[[i]]
      ## 'col' symbols with a 'bg'-colored interior (where available) :
      points(ix[i], iy[i], pch = pc, col = col, bg = bg, cex = cex)
      if(cextext > 0)
          text(ix[i] - 0.3, iy[i], pc, col = coltext, cex = cextext)
    }
  }

pchShow()

```

```{r abline legend}
col.v=c("blue","red","blue","red","red","blue","red","blue")
plot(width~length, pch=as.character(sex), data=indexfinger,col=col.v)

abline(lm(width~length, data=indexfinger, subset=sex=="M"), lty=1, col="blue")

abline(lm(width~length, data=indexfinger, subset=sex=="F"), lty=1, col="red")

legend(x=6, y=2.4, legend=c("Male", "Female"), lty=1:2, col=c("blue","red"))

```

